%-------------------------
% Resume in Latex
% Author : Himanshu Garg
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{ #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\Large Himanshu Garg}} & Email :  \href{mailto:garg_himanshu@outlook.com}{garg\_himanshu@outlook.com}\\
  \href{https://linkedin.com/in/garg-himanshu}{ \textbf{linkedin}.com/in/garg-himanshu} \textbullet{}
  \href{https://github.com/merrcury}{\textbf{github}.com/merrcury}& Mobile :  +91-816-845-5748 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Kurukshetra University}{Kurukshetra, India}
      {B.Tech in Computer Science \& Engineering; GPA 7.0/10}{Jul 2017 - Jun 2021}
      
    \resumeSubheading
      {D.A.V. Centenary Public School}{Pehowa, India}
      {Non-Medical ; Central Board of Secondary Education; 87.8\%
}{Mar 2016 - May 2017
}
  \resumeSubHeadingListEnd

%--------SKILLS------------
\section{Skill summary}
  \resumeSubHeadingListStart
    \resumeSubItem{Languages}
    {: Python, C++, C\#, NoSQL, SQL, Bash}
    \resumeSubItem{Libraries \& Framework}
    {: H20, Scikit, NLTK, Prophet, SpaCy, LAMP}
    \resumeSubItem{Tools}
    {: Docker, GIT, MongoDB, MySQL}
    \resumeSubItem{Platforms}
    {: Linux, Windows, GCP, Firebase, Azure, IBM Watson, Heroku, GitHub, IPython, Raspberry}
    \resumeSubItem{Soft Skills}
    {: Leadership, Event Management, Writing, Public Speaking, Time Management}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Crio.Do}{Remote}
      {Teaching Assistant - Part time}{Jan 2020 - Present}
      \resumeItemListStart
        \resumeItem{}
          {Assisted learners in \textbf{Linux \& Python} and Assuring Quality Responses.}
        \resumeItem{}
          {Helped Core team with issue tracking and tackling.}
      \resumeItemListEnd

    \resumeSubheading
      {Career Launcher}{Remote}
      {Machine Learning Intern}{Jul 2019 - Aug 2019}
      \resumeItemListStart
      \resumeItem{}
          {Researched \& Studied \textbf{Financial Market} as a Machine Learning Use Case with Modern Theories.}
        \resumeItem{}
          {Data Science Reports driven work stressed on \textbf{Visualization \& Analysis} with Machine Learning}
      \resumeItemListEnd

    \resumeSubheading
      {IBM Business Partners}{Chandigarh}
      {Artificial Intelligence Intern}{Jun 2019 - Jul 2019}
      \resumeItemListStart
        \resumeItem{}
          {Worked on IBM tools, Mainly concentrated on \textbf{IBM Cloud \& IBM Watson}.}
        \resumeItem{}
          {Day to Day Job includes study \textbf{Conversational AI} \& implement that with distinct NLP techniques.}
        \resumeItem{}
          {Got certified for Python, Machine Learning \& Chat-bots by clearing testimonials.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd



%---------------------------------------
\section{Achievements}
 \resumeSubHeadingListStart
   \resumeSubItem{Top 8 in Microsoft India Innovation Series,} {A National Level Hackathon by Microsoft}
   \resumeSubItem{Top 9 in Electrothon out of 110 Teams,} {A National Level Hackathon by NIT Hamirpur}
    \resumeSubItem{1st Runner Up at Hack-N-Cody,} {A National Level Hackathon by UIET, Kurukshetra University}
    \resumeSubItem{Winner at AutumnHacks,} {A National Level Hackathon by LPU, Jalandhar}
    \resumeSubItem{1st Runner Up at Hackshetra'19,} {A National Level Hackathon by NIT, Kurukshetra}
    \resumeSubItem{Special Recognition Award at Infosys Digital Makeathon 2.0,} {An Annual National level Hackathon of Infosys}
    \resumeSubItem{Winner of Innovator'16,} {An annual Inter-School competition in D.A.V. Schools of State}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{CursAR}
      {An AR APP built in Unity using C\#. It helps student visualize 2D figures in 3D interactions.}
    \resumeSubItem{AI for Blind}
      {A Multi-functional App Suite help blind in various activities like Indoor \& Outdoor Navigation, Communicating(help them with Facial Expression \& Mood) through bluetooth or wired headset.}
    \resumeSubItem{City Surveillance System}
      {A Real-time automated system for identifying criminals, missing persons and recognizing stolen vehicle with a very competitive alert and navigation system for local Police. 
      }
    \resumeSubItem{Traffic Volume Prediction}
      {Predicting Traffic Volume with Root Mean Squared Logarithmic Error as low as 0.04.}
    \resumeSubItem{Investing Guide}
      {A Multi-functional Suite for building the most profitable or most versatile investing portfolio with automated buying \& selling of stocks keeping account of history at every stage.}
    \resumeSubItem{Chat-bot}
    {A Marvel Movies Quiz Chat-bot built \& deployed on Facebook, Twitter \& Telegram.}
    \resumeSubItem{NLP Model for Complaint Management System}
     {A Real-time NLP Classifier for deciding priority order of a complaint \& filter out complaint with explicit content \& with excessive emotions integrated in Android APP \& Website.}
  \resumeSubHeadingListEnd

\end{document}